They are Very Smart: Genetic-Algorithm-Based Pathfinding in Games

### 2018-12-12 paper.tex
Paper: fix Zombunny capitialization

\subsection{Code overview}
\subsubsection{Hyperparameters}
The hyperparameters relevant to playing with how the games are the constants at
the top of \path{Assets/Scripts/Evolution/Genome.cs}, \texttt{HEALTH\_SCALE},
\texttt{DAMAGE\_SCALE}, and \texttt{MOVEMENT\_SCALE}; and at the top of
\path{Assets/Scripts/TowerDefence/Level/GenomeManager.cs}, with
\texttt{POPULATION\_SIZE}, \texttt{MUTATION\_RATE}, \texttt{GROWTH\_RATE},
\texttt{SPAWN\_DELAY}, and \texttt{STARTING\_TOTAL}. The scale constants in
\path{Genome.cs} change how health, speed, and damage are scaled relative to
each other. \texttt{POPULATION\_SIZE} represents the number of genomes (and
therefore zombunnies) in every generation. \texttt{MUTATION\_RATE} determines how
much variance there is in every mutation operation. \texttt{GROWTH\_RATE}
Determines how much combined speed, health, and damage is available to be
distributed. \texttt{SPAWN\_DELAY} determines how much time passes between spawns
in waves. \texttt{STARTING\_TOTAL} determines the total number of stats available
to the zombunnies at the start of the game.

>>>>

\subsection{Code overview}
\subsubsection{Hyperparameters}
The hyperparameters relevant to playing with how the games are the constants at
the top of \path{Assets/Scripts/Evolution/Genome.cs}, \texttt{HEALTH\_SCALE},
\texttt{DAMAGE\_SCALE}, and \texttt{MOVEMENT\_SCALE}; and at the top of
\path{Assets/Scripts/TowerDefence/Level/GenomeManager.cs}, with
\texttt{POPULATION\_SIZE}, \texttt{MUTATION\_RATE}, \texttt{GROWTH\_RATE},
\texttt{SPAWN\_DELAY}, and \texttt{STARTING\_TOTAL}. The scale constants in
\path{Genome.cs} change how health, speed, and damage are scaled relative to
each other. \texttt{POPULATION\_SIZE} represents the number of genomes (and
therefore Zombunnies) in every generation. \texttt{MUTATION\_RATE} determines how
much variance there is in every mutation operation. \texttt{GROWTH\_RATE}
Determines how much combined speed, health, and damage is available to be
distributed. \texttt{SPAWN\_DELAY} determines how much time passes between spawns
in waves. \texttt{STARTING\_TOTAL} determines the total number of stats available
to the Zombunnies at the start of the game.
